%-------------------------
% Resume in LaTeX
% Author: Andrew Steinheiser
% Based off of: https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Andrew Steinheiser} \\ \vspace{1pt}
    \small 623-208-9405 $|$
    \href{mailto:me@iamandrew.io}{\underline{me@iamandrew.io}} $|$
    \href{https://linkedin.com/in/andrew-steinheiser}{\underline{linkedin/andrew-steinheiser}} $|$
    \href{https://github.com/asteinheiser}{\underline{github/asteinheiser}} $|$
    \href{https://iamandrew.io}{\underline{iamandrew.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Aug. 2014 -- Dec. 2017}
      {Bachelor of Science in Computer Science}{Tempe, AZ}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, HTML/CSS, SQL, Go} \\
     \textbf{Frameworks}{: React, React Native, GraphQL, Next.js, NestJs, Node.js, SST, Express, XState, Tailwind, Shadcn} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Terraform, Datadog, Sentry, Jest, Vitest, Storybook} \\
     \textbf{DB/CMS/Index}{: PostgreSQL, DynamoDB, MongoDB, Firestore, Contentful, Hygraph, Algolia, Typesense} \\
     \textbf{AWS Tools}{: Lambda, API Gateway, Event Bridge, S3, SQS, SES, EC2, ECS, IAM, Step Functions, Route 53} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{June 2021 -- Mar. 2025}
      {Sibi}{Gilbert, AZ (Hybrid)}
      \resumeItemListStart
        \resumeItem{Collaborated with product, design and program teams to build, test and evaluate features for the Sibi platform.}
        \resumeItem{Strategically implement and control feature rollouts for different user groups across the web and mobile apps.}
        \resumeItem{Worked across teams to develop solutions for each of the three frontends written in React or React Native.}
        \resumeItem{Primary developer of the mobile app which saw over \$50,000 in purchasing volume every week.}
        \resumeItem{Architected and maintained microservices on AWS (SST), utilizing Lambda, Event Bridge, DynamoDB and SQS.}
        \resumeItem{Contributed to the migration of legacy APIs and DBs to a new microservice architecture.}
        \resumeItem{Frequently and successfully spearheaded data migration scripts, including a 7 million row migration.}
        \resumeItem{Mentored junior developers from day one to delivering reliable PRs using TypeScript, React, GraphQL and SST.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{Sep. 2020 -- June 2021}
      {Magic Leap}{Fort Lauderdale, FL (Remote)}
      \resumeItemListStart
        \resumeItem{Read internal documentation and implemented key user authentication APIs to support the MagicVerse platform.}
        \resumeItem{Developed APIs to store data for MagicVerse users and their settings written in NestJs (TypeScript).}
        \resumeItem{Worked on a middleware service for managing complex permissions leveraging Istio (Envoy) running OPA policies.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Mar. 2019 -- Sep. 2020}
      {Sibi}{Gilbert, AZ (Hybrid)}
      \resumeItemListStart
        \resumeItem{Rewrote and maintained the React Native mobile application responsible for about 20\% of purchases on platform.}
        \resumeItem{Helped reduce development time by refactoring and reusing code between the React web and mobile applications.}
        \resumeItem{Worked on a native iOS experiment leveraging augmented reality to allow users to "place" items in their homes.}
        \resumeItem{Made updates and improvements to the federated GraphQL API (TypeScript) to support feature requests.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Dec. 2017 -- Mar. 2019}
      {Fyresite}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Worked directly with clients to build spec sheets, wireframes, timelines, and pricing estimates for features.}
        \resumeItem{Architected and implemented fullstack web and mobile applications using React, React Native, MySQL and AWS.}
        \resumeItem{Solely developed the Clutch mobile app, which was used by over 1,000+ members of DZ at ASU for their events.}
        \resumeItem{Built Zinkn, a rideshare app that matched elderly users with licensed care professionals via AWS Step Functions.}
        \resumeItem{Worked on Ten Minutes, a HIPAA compliant mobile app that provided situational information about anesthesia.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{Nov. 2014 -- Nov. 2017}
      {Citrix - Octoblu}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Pair programmed with senior developers to build features for the web IoT platform using React.js and AWS.}
        \resumeItem{Deployed changes for our web apps and connectors, such as app.octoblu.com and meshblu-connector-skype.}
        \resumeItem{Helped support users via Intercom chat to make onboarding and setting up custom automations easier.}
        \resumeItem{Created over 15 blog posts showcasing automations using the IoT platform, which can be seen on \href{https://www.hackster.io/andrewstein/}{\underline{hackster.io}}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AmpSkate} $|$ \emph{TypeScript, React, Next.js, Postgres, Docker, AWS ECS, Terraform}}{Dec. 2021 - June 2023}
          \resumeItemListStart
            \resumeItem{A grassroots web app to foster community, provide information and teach people how to learn longboard tricks.}
            \resumeItem{Worked asynchronously with a UI developer from Italy and 2 marketing and content creators from Los Angeles.}
            \resumeItem{Architected and implemented the web app, API and CMS that served over 500 active users per month.}
            \resumeItem{Provided scopes, timelines and pricing estimates for feature development as well as evaluation of 3rd party APIs.}
            \resumeItem{\href{https://www.instagram.com/amp\_\_skate}{\underline{instagram/amp\_\_skate}}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{React RPG} $|$ \emph{JavaScript, React, React Native, Redux, HTML/CSS}}{Sep. 2018 -- Mar. 2022}
          \resumeItemListStart
            \resumeItem{Created a 2D top-down open-source RPG in React from scratch using Redux and some CSS animations/tricks.}
            \resumeItem{Has a story mode as well as a randomly generated infinite mode, where maps and monsters are created on the fly.}
            \resumeItem{10+ people contributed over the course of 4 years, and the project now has 350+ stars and 50+ forks on GitHub.}
            \resumeItem{One of the top maintainers of Redux personally helped identify a longstanding bug in the core Redux store code.}
            \resumeItem{A group at Uni. of Auckland used this project for their CSE732 class by modifying the game to mimic DnD:5e.}
            \resumeItem{Try it out at \href{https://react-rpg.com}{\underline{react-rpg.com}} or check out the \href{https://github.com/ASteinheiser/react-rpg.com}{\underline{github}} for links to blog posts where I describe my process and goals.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------LEADERSHIP-----------
\section{Leadership}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \resumeSubheading
      {SunSesh AZ}{Feb. 2021 - Present}
      {Founder and Organizer}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Host a weekly longboard dancing/freestyle meetup in Tempe, AZ, partnered with Loaded and Orangatang.}
        \resumeItem{Encourage and provide resources for local longboard enthusiasts that are new to the sport.}
        \resumeItem{Push members of the community to share their knowledge through events like downhill clinics and jam sesssios.}
        \resumeItem{Moderate a discord server with the goal of sharing tips, selling gear, etc. for over 100 members local to the valley.}
        \resumeItem{\href{https://www.instagram.com/sunsesh\_az}{\underline{instagram/sunsesh\_az}}}
      \resumeItemListEnd
    \resumeSubheading
      {SAVG Thread}{June 2017 - Aug. 2018}
      {Founder and Designer}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Launched a clothing brand by collaborating with local photographers, models, artists and clothing designers.}
        \resumeItem{Created and sold t-shirts with custom modifications, such as zippers, bleaching, etc. via my SquareSpace website.}
        \resumeItem{Worked with a local manufacturer to finalize my kimono pattern and produce a line of 25, which sold for \$139/ea.}
        \resumeItem{Sold multiple custom lines of t-shirts, including a commission for a local artist for their short film.}
        \resumeItem{\href{https://www.instagram.com/savgthread}{\underline{instagram/savgthread}}}
      \resumeItemListEnd
   }}
\end{itemize}

%
%-----------AWARDS-----------
\section{Awards}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{2024 Most Innovative Project}{ @ Sibi HackAIthon - Sibi, Gilbert, AZ} \\
    \textbf{2023 Runner Up}{ @ Sibi HackAIthon - Sibi, Gilbert, AZ} \\
    \textbf{2017 Cisco IoT Finalist}{ @ Smart City Hack - City of Phoenix, Phoenix, AZ} \\
    \textbf{2017 Best Use of AWS}{ @ HackAz - University of Arizona, Tucson, AZ} \\
    \textbf{2016 1st Place}{ @ Startup Weekend - University of Arizona, Tucson, AZ} \\
    \textbf{2016 Best Beginner Hack}{ @ HackAz - University of Arizona, Tucson, AZ} \\
    \textbf{2015 Nodebots Champion}{ @ Nodebots - Heatsync Labs, Mesa, AZ} \\
   }}
\end{itemize}

%-------------------------------------------
\end{document}